Percolation Analysis – Building a Package

### 2019-07-31 paper.Rmd
skriptnamen

sNL_shape <- readOGR(dsn="shape_files/alle_Schnitt-Fundstellen.shp"

library(maptools)
library(rgdal)
library(stringr)
library(igraph)

source("R/create_nodes_list_d.v4.7.R")
percolateNodes(data = data, radius_values = 10, limit = 500, radius_unit = 1)

source("R/clustering_script.v3.6.R")
percolate()

percolate2(data = data, radius_values = 10, limit = 500, radius_unit = 1)

source("R/mapping_clusters.v4.12.R")
mapClusters(data = data, shape = sNL_shape)

>>>>

library(maptools)
library(rgdal)
library(stringr)
library(igraph)
sNL_shape <- readOGR(dsn="shape_files/alle_Schnitt-Fundstellen.shp")

source("R/nodes_clust.R")
percolate2(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20)

source("R/map_clust.R")
mapClusters(data = data, radius_values = 10, limit = 500, radius_unit = 1, upper_radius = 200, lower_radius = 20, step_value = 20, shape = sNL_shape, map_name = "sNL-Karte")
